---
title: "Empiriepraktikum"
lang: en
---
::: {.grid}
::: {.g-col-4}
![](assets/images/logo.svg)
:::
::: {.g-col-8}
The Empiriepraktikum seminar, a.k.a. EMPRA, is a practical course focused on the independent planning, implementation, and critical analysis of empirical research. Participants develop skills in formulating research questions, creating and testing hypotheses, designing research plans, conducting empirical studies, and analyzing and critically discussing the results. The seminar integrates project experiences to enhance the students' ability to conduct and present their own research findings effectively.
:::
:::

```{r}
#| echo: FALSE
#| warning: FALSE
#| message: FALSE
source("submission_utils.R")

empra_year <- 2025
submissions <- load_years_submissions(empra_year)
```



## EMPRA Conference 2025

### When and Where
The Empra conference will take place on **Friday, January 24th** from 10 to 14 o’clock. The venue is **M3N/2.32** plus the foyer in front of this lecture room.

### Preliminary program

* Welcome address (Prof. Carbon).
* Keynote talk (Stefan Breitschaft, a former student at the University of Bamberg who is now working at BMW Group).
* Talk session I.
* Poster session I.
* Talk session II.
* Poster session II. 


### Talks
```{r talks-2025-en, results='asis'}
#| echo: FALSE
#| warning: FALSE
#| message: FALSE
list_submissions(submissions, "talk", rmarkdown::metadata$lang)
```

### Posters
```{r posters-2025-en, results='asis'}
#| echo: FALSE
#| warning: FALSE
#| message: FALSE
list_submissions(submissions, "poster", rmarkdown::metadata$lang)
```
